IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex
Fix broken
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\subsection{External Effects}
\label{sec:extensions:external}
Our embedding assumes that the target language not have any
primitives that can external-world effects.
%
Indeed, as discussed in Section~\ref{sec:real}, part of the challenge
when considering real languages is precisely imposing this restriction
on the concrete implementation.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, code in our modified IFC browser must load resources or
perform XHR to be useful.

>>>>

\subsection{External Effects}
\label{sec:extensions:external}
Our embedding assumes that the target language not have any
primitives that can induce external-world effects.
%
As discussed in Section~\ref{sec:real}, imposing this restriction
can be challenging.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, code in an IFC browser must load resources or
perform XHR to be useful.
